Almost compatible functions and infinite length games

### 2016-09-06 articles/almost-compatible-functions-and-topological-games/article.tex
improve the final question, reflecting reviewer feedback
more work on the paper ending

  \begin{corollary}[\(V=L\)]
    \(\alcompSP{\kappa}\) for all cardinals \(\kappa\).
  \end{corollary}

@@

  Note that Question \ref{mainQuestion} remains unsolved; however,
  our results have revealed that we cannot hope to find a \(ZFC\)
  counterexample where \(X=\oneptlind\kappa\). This is
  because if we also assume \(V=L\), it follows that
  \(\alcompSP{\kappa}\) and therefore
  \(\pl F\kmarkwin2\menGame{\oneptlind\kappa}\)
  for every cardinal \(\kappa\).
  Although, one may consider the following question.

  \begin{question}
    Is there a model of \(ZFC\) where both
    \(\pl F\kmarkwin2\menGame{\oneptlind{\aleph_{\omega+1}}}\) and
    \(\alcompSP{\aleph_\omega}\) fail?
  \end{question}

>>>>

  \begin{corollary}[\(V=L\)]\label{alcompSPunderV=L}
    \(\alcompSP{\kappa}\) for all cardinals \(\kappa\).
  \end{corollary}

@@

  We conclude by returning our attention to Question \ref{mainQuestion},
  which asks whether there exists a space for which the second player
  \(\pl F\) in the Menger game \(\menGame{X}\) has a winning strategy
  without a winning \(2\)-mark.

  \begin{question}
    Does
    \(\pl F\kmarkwin2\schFillIntGame{\kappa}\) hold for all cardinals
    \(\kappa\) in ZFC?
  \end{question}

  If not, the model producing \(\kappa>\aleph_\omega\) where
  \(\pl F\notkmarkwin2\schFillIntGame{\kappa}\) yields a positive
  answer to Question \ref{mainQuestion}:
  \(X=\oneptlind{\kappa}\). On the other hand, under \(V=L\)
  Corollary \ref{alcompSPunderV=L} shows that
  \(\alcompSP{\kappa}\) and therefore
  \(\pl F\kmarkwin2\menGame{\oneptlind\kappa}\)
  for every cardinal \(\kappa\), so a more exotic example than
  \(X=\oneptlind{\kappa}\) would be required to
  answer Question \ref{mainQuestion} in \(ZFC\).

  Solving the following weaker question would not answer Question
  \ref{mainQuestion} by itself, but an solution would be interesting nonetheless.

  \begin{question}
    Does
    \(\pl F\kmarkwin2\schFillGame{\kappa}\) hold for all cardinals
    \(\kappa\) in ZFC?
  \end{question}
